Supporting Information

### 2021-09-02 vertical-thermal-review.Rmd
word count

@@

>>>>

Text | word count | other | n
---|---|-----|--------------------
Total word count (excluding summary, references and legends) | 	8565 |	No. of figures | 	5 (all colour)
Summary|  	183 | 	No. of Tables | 	2  
Introduction|	497 |	No of Supporting Information files | 	6
Review of vertical gradients |	5976	||	 
Implications |	1753	 ||
Conclusions |	156	||
Acknowledgments | ##	||

@@

## Acknowledgements
Thanks to ...., the ForestGEO Ecosystems & Climate lab at SCBI for helpful discussion.
Funding was provided by the Smithsonian Institution, ....
